---
output: pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
# setwd("figures")
source("../scripts/99_utils.R")
```

```{r ```{r 07_model_selection, fig.height=3, echo=FALSE}

# setwd("figures")
ids <- test <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()

hu4 <-  LAGOSNEgis::query_gis("HU4", "ZoneID", ids$hu4_zoneid) %>%
  st_cast(to = "MULTIPOLYGON") %>%
  left_join(ids, by = c("ZoneID" = "hu4_zoneid"))

n_cat  <- 6
colors <- c("#FFFFFF", viridisLite::viridis(n_cat - 1))
hu4    <- mutate(hu4, 
            n_cat = cut(hu4$n, breaks = 
                          classInt::classIntervals(hu4$n, n = n_cat)$brks))
hu4 <- dplyr::filter(hu4, !is.na(n_cat))

# hist(hu4$n, n = 20)
# table(as.character(dt$hu4_zoneid))

lg <- lagosne_load("1.087.1")

# ep <- left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid), 
#                 summarize(
#                   group_by(dplyr::select(lg$epi_nutr, lagoslakeid, tp, chla), 
#                            lagoslakeid), 
#                   tp = median(tp, na.rm = TRUE), 
#                   chla = median(chla, na.rm = TRUE)), 
#                 by = "lagoslakeid") %>%
#   tidyr::drop_na() 

dt <- readRDS("../data/dt.rds") %>%
  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", 
                "ag_pct", "phosphorus_fertilizer_use", "soybeans")

# hist(as.vector(table(dt$hu4_zoneid)))  
# good_hu4s <- group_by(dt, hu4_zoneid) %>% 
#   tally() %>%
#   dplyr::filter(n > 220)  
# dt <- dplyr::filter(dt, hu4_zoneid %in% good_hu4s$hu4_zoneid)
# dt <- dplyr::filter(dt, tp < 500 & chla < 150)

# create alpha sample size weightings
dt <- left_join(dt, ungroup(count(group_by(dt, hu4_zoneid))), 
                by = "hu4_zoneid") %>%
  dplyr::filter(n >= 5) %>%
  mutate(n = n / max(n, na.rm = TRUE))
  
# join iws ag
# dt <- left_join(dt, ungroup(dplyr::select(mutate(
#   group_by(lg$iws.lulc, lagoslakeid), 
#   ag_pct = sum(iws_nlcd2011_pct_81,
#                            iws_nlcd2011_pct_82, na.rm = TRUE)), 
#   lagoslakeid, ag_pct))
#   )

# create hu4 labels
centroid_xy <- sf::st_as_text(sf::st_geometry(sf::st_centroid(hu4[,"ZoneID"])))
extract_coords <- function(messy_centroid){
  res <- stringr::str_split(messy_centroid, "\\(", simplify = TRUE)[2]
  res <- stringr::str_split(res, "\\)", simplify = TRUE)[1]
  stringr::str_split(res, " ", simplify = TRUE)
}
coords <- data.frame(matrix(
            as.numeric(unlist(lapply(centroid_xy, extract_coords))),
            ncol = 2, byrow = TRUE), stringsAsFactors = FALSE)
names(coords) <- c("x", "y")
coords$ZoneID <- gsub("HU4_", "", hu4[,"ZoneID"]$ZoneID)

plot_grid(
  ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    # geom_point() +
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # scale_y_log10() + scale_x_log10() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct, NLCD 2011)", 
         y = "TP")  +
    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300)),
  ggplot() +
    geom_sf(data = hu4, aes(fill = n_cat)) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) + 
    scale_fill_manual(values = colors, levels(hu4$n_cat)), 
  rel_heights = c(0.6, 1), labels = "AUTO"
)
``` 

```{r brms_stan}
library(brms)
library(tidybayes)

dt        <- readRDS("../data/dt.rds") %>% 
  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", 
                "ag_pct", "phosphorus_fertilizer_use", "soybeans")
names(dt) <- gsub("_", "v", names(dt))
dt        <- dplyr::filter(dt, !is.na(phosphorusvfertilizervuse), 
                    !is.na(soybeans))

# linear
model_form <- bf(tp ~ agvpct)
fit0 <- brm(formula = model_form, data = dt, 
           family = gaussian())

get_variables(fit0)
plot(fit0, pars = "agvpct")

# linear re
model_form <- bf(tp ~ (1 + agvpct | hu4vzoneid))
fit <- brm(formula = model_form, data = dt, 
           family = gaussian())

# non-linear re
model_form <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + 
                   (1|hu4vzoneid), 
                 nl = TRUE)
fit1 <- brm(formula = model_form, data = dt, 
           family = gaussian())

# non-linear re w/ 2nd level coeffs
model_form2 <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + phosphorusvfertilizervuse + soybeans +
                   (1|hu4vzoneid), 
                 nl = TRUE)
fit2 <- brm(formula = model_form2, data = dt, 
           family = gaussian())
---

# pull global distribution (lower, mean, upper)
# get_variables(fit0)
global_dist <- spread_draws(fit0, b_agvpct) %>%
    mutate(hu4vzoneid = "global") %>%
    group_by(hu4vzoneid) %>%
    do(tibble::as_tibble(t(quantile(.$b_agvpct, c(0.05, 0.5, 0.95)))))

# pull hu4 distribution (lower, mean, upper)
hu4_dist <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
  dplyr::filter(term == "agvpct") %>%
  group_by(hu4vzoneid) %>%
  do(tibble::as_tibble(t(quantile(.$r_hu4vzoneid, c(0.05, 0.5, 0.95))))) %>%
  mutate(signif = case_when(`5%` > 0 ~ TRUE))

all_dist <- bind_rows(global_dist, hu4_dist)

ggplot(data = all_dist) +
  geom_point(aes(x = hu4vzoneid, y = `50%`)) +
  geom_errorbar(aes(ymin = `5%`, ymax = `95%`, x = hu4vzoneid, color = signif)) +
  geom_hline(yintercept = 0) +
  coord_flip()

hu4_signif <-  LAGOSNEgis::query_gis(
  "HU4", "ZoneID", dplyr::filter(hu4_dist, signif)$hu4vzoneid) %>% 
  st_cast(to = "MULTIPOLYGON")

# pull 2nd level covariate distributions
get_variables(fit2)
# spread_draws(fit, b_Intercept)

plot(fit, pars = "agvpct")

test <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
  dplyr::filter(term == "agvpct") %>%
  group_by(hu4vzoneid) %>%
  summarise(agvpct_effect = median(r_hu4vzoneid))
quantile(test$agvpct_effect, c(0.05, 0.5, 0.95))


m <- add_fitted_draws(dt, b_)

spread_draws(fit, Intercept)
spread_draws(fit1, bagvpct[hu4vzoneid,])

ggplot() + 
    stat_lineribbon(data = m, 
                             aes(x = retention_time_yr, 
                                 y = estimate), .prob = c(0.95), 
                    fill = "grey", color = "black", alpha = 0.5)


+ 
    geom_point(data = nes, aes(x = retention_time_yr, 
                               y = p_percent_retention), 
               size = 0.6, color = "black") + 
    scale_x_log10() + ylim(0, 1) +
    scale_fill_discrete("grey") + 
    theme_pred() + 
ylab("P retention") + xlab("Residence time (yr)") + ggtitle("A.")

stat_lineribbon()
stancode(fit1)  
    
m <- tidybayes::recover_types(fit1)

bayes_results = m %>%
  spread_draws()
%>%
  median_qi(estimate = condition_mean) %>%
  to_broom_names() %>%
  mutate(model = "Bayes")
bayes_result

---
loo1 <- loo(fit1)
loo2 <- loo(fit2)
loo_compare(loo1, loo2)  
---



  
fit <- brm(formula = model_form, data = dt, 
           family = gaussian())

summary(fit2)
marginal_effects(fit2)
conditions <- data.frame(hu4vzoneid = unique(dt$hu4vzoneid)[1])
rownames(conditions) <- unique(dt$hu4vzoneid)[1]
me_zone <- marginal_effects(fit, conditions = conditions, 
                            re_formula = NULL, method = "predict")
ran_ef <- as.data.frame(ranef(fit)$hu4vzoneid) %>%
  mutate(zoneid = rownames(.)) %>%
  dplyr::filter(zoneid == unique(dt$hu4vzoneid)[1])

plot(me_zone, ncol = 1)$agvpct + 
  ggtitle(unique(dt$hu4vzoneid)[1]) +
  geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
                broom::tidy(fit)$estimate[1])

```